Robust data management for high through-put light sheet microscopy of whole mouse brains

### 2015-02-05 latex-style-files-spie-manuscript/manuscript_merged.tex
new origin graph of microscope characterisation marcels name is corrected

\author{M. Caroline M\"{u}llenbroich,\supscr{a,b} Ludovico Silvestri, \supscr{a,c} Leonardo Onofri,\supscr{e} Irene Costantini,\supscr{a} Marcel Van t'Hoff,\supscr{f} Leonardo Sacconi,\supscr{a,c} Giulio Iannello,\supscr{e} Francesco S. Pavone,\supscr{a,b,c,d}  }

\affiliation{\supscrsm{a}European Laboratory for Non-linear Spectroscopy (LENS), University of Florence, Italy\\
\supscrsm{b}Department of Physics and Astronomy, University of Florence, Italy\\
\supscrsm{c}National Institute of Optics, National Research Council, Italy\\
\supscrsm{d}International Center for Computational Neurophotonics (ICON Foundation), Italy\\
\supscrsm{e}Integrated Research Centre, University Campus Bio-Medico of Rome, Italy\\
\supscrsm{f}Distrio, Murmex}

@@

	\subsection{Contrast}

	\subsection{Signal-to-noise ratio}

	\subsection{Optical sectioning}

>>>>

\author{M. Caroline M\"{u}llenbroich,\supscr{a,b} Ludovico Silvestri, \supscr{a,c} Leonardo Onofri,\supscr{e} Irene Costantini,\supscr{a} Marcel van 't Hoff,\supscr{a,b,f} Leonardo Sacconi,\supscr{a,c} Giulio Iannello,\supscr{e} Francesco S. Pavone,\supscr{a,b,c,d}  }

\affiliation{\supscrsm{a}European Laboratory for Non-linear Spectroscopy (LENS), University of Florence, Italy\\
\supscrsm{b}Department of Physics and Astronomy, University of Florence, Italy\\
\supscrsm{c}National Institute of Optics, National Research Council, Italy\\
\supscrsm{d}International Center for Computational Neurophotonics (ICON Foundation), Italy\\
\supscrsm{e}Integrated Research Centre, University Campus Bio-Medico of Rome, Italy\\
\supscrsm{f}Distrio, Amsterdam, The Netherlands}

@@

	\begin{figure}
   \begin{center}
   \begin{tabular}{c}
   \includegraphics[width=\textwidth]{origin.eps}
   \end{tabular}
   \end{center}
   \caption{\label{fig:origin} Optical characterisation. (A) Exemplary lateral and axial intensity profiles of sub-resolution beads and fits to Gaussian. (B) For each unit 10 bead profiles were fitted in all three dimensions and their FWHM was averaged. (C) The signal to noise ratio.} 
   \end{figure}
